Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-06-21 Supplemental-Material-A-Annotated-Analysis.Rmd
initial amelia implementation
Update Supplemental-Material-A-Annotated-Analysis.Rmd

PIDout <- gsub("PP_", "", dtS1RedInfo$rowNamesOut) %>% as.numeric
TIDout <- gsub("t_", "", dtS1RedInfo$colNamesOut) %>% as.numeric

dtS1Red <- dtS1$full %>%
  filter(
    !PID %in% PIDout,
    !TIDnum %in% TIDout
  ) %>%
  mutate(TIDnum = as.numeric(factor(TIDnum)))
rm(PIDout, TIDout)

dtS1AvailabilityRedKbl <- dtS1RedInfo$reducedMatrix
dtS1AvailabilityRedKbl[1:ncol(dtS1AvailabilityRedKbl)] <- lapply(dtS1AvailabilityRedKbl[1:ncol(dtS1AvailabilityRedKbl)], function(x) {
    cell_spec(x,
              bold = FALSE,
              color = "white",
              background = ifelse(x == 1, "green", "red")
              )
})
kbl(
  dtS1AvailabilityRedKbl,
  format = "html",
  escape = FALSE,
  align = "c",
  booktabs = TRUE,
  caption = "Study 1: FinalData Availability" # complete caption for main document
) %>%
  kable_classic(
    full_width = FALSE,
    lightable_options = "hover",
    html_font = "Cambria"
  ) %>%
  scroll_box(width = "100%", height = "500px")
```

@@

PIDout <- gsub("PP_", "", dtS2RedInfo$rowNamesOut) %>% as.numeric
TIDout <- gsub("t_", "", dtS2RedInfo$colNamesOut) %>% as.numeric

dtS2Red <- dtS2$full %>%
  filter(
    !PID %in% PIDout,
    !TIDnum %in% TIDout
  ) %>%
  mutate(TIDnum = as.numeric(factor(TIDnum)))
rm(PIDout, TIDout)

@@

```{}

>>>>

PIDout <- gsub("PP_", "", dtS1RedInfo$rowNamesOut) %>% as.numeric
TIDout <- gsub("t_", "", dtS1RedInfo$colNamesOut) %>% as.numeric
TIDInRed <- gsub("t_", "", dtS1RedInfo$colNamesIn) %>% as.numeric
TIDIn <- seq(min(TIDInRed), max(TIDInRed), 1)

dtS1Red <- dtS1$full %>%
  filter(
    !PID %in% PIDout,
    TIDnum %in% TIDIn
  ) %>% 
  select(TIDnum) %>%
  mutate(TIDnum = TIDnum - min(TIDnum))
rm(PIDout, TIDout, TIDInRed, TIDIn)

dtS1AvailabilityRedKbl <- dtS1RedInfo$reducedMatrix
dtS1AvailabilityRedKbl[1:ncol(dtS1AvailabilityRedKbl)] <- lapply(dtS1AvailabilityRedKbl[1:ncol(dtS1AvailabilityRedKbl)], function(x) {
    cell_spec(x,
              bold = FALSE,
              color = "white",
              background = ifelse(x == 1, "green", "red")
              )
})
kbl(
  dtS1AvailabilityRedKbl,
  format = "html",
  escape = FALSE,
  align = "c",
  booktabs = TRUE,
  caption = "Study 1: Final Data Availability" # complete caption for main document
) %>%
  kable_classic(
    full_width = FALSE,
    lightable_options = "hover",
    html_font = "Cambria"
  ) %>%
  scroll_box(width = "100%", height = "500px")
```

@@

PIDout <- gsub("PP_", "", dtS2RedInfo$rowNamesOut) %>% as.numeric
TIDout <- gsub("t_", "", dtS2RedInfo$colNamesOut) %>% as.numeric
TIDInRed <- gsub("t_", "", dtS2RedInfo$colNamesIn) %>% as.numeric
TIDIn <- seq(min(TIDInRed), max(TIDInRed), 1)

dtS2Red <- dtS2$full %>%
  filter(
    !PID %in% PIDout,
    TIDnum %in% TIDIn
  ) %>% 
  select(TIDnum) %>%
  mutate(TIDnum = TIDnum - min(TIDnum))
rm(PIDout, TIDout, TIDInRed, TIDIn)

@@

```{r MiMain3mpca}
library(Amelia)

dtMain3mpcaMI<- dtMain3mpca %>%
  select(
    -date,
    -TID,
    -week
  ) %>%
  as.data.frame

a.out <- amelia(dtMain3mpcaMI, m = 20, ts = "TIDnum", idvars = c("ID", "PID", "study"))
